An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-11 paper.tex

  \caption{Descriptions of the 47 markers used in this study.}

@@

  \begin{tabular}{rlll}

@@

    Number & Label & Name & Description \\

@@

    1  & LHEAD & Left head                             & Just above the ear, in the middle. \\
    2  & THEAD & Top head                              & On top of the head, in line with the LHEAD and RHEAD. \\
    3  & RHEAD & Right head                            & Just above the ear, in the middle. \\
    4  & FHEAD & Forehead                              & Between line LHEAD/RHEAD and THEAD a bit right from center. \\
    5  & C7    & C7                                    & On the 7th cervical vertebrae. \\
    6  & T10   & T10                                   & On the 10th thoracic vertbrae. \\
    7  & SACR  & Sacrum bone                           & on the scacral bone. \\
    8  & NAVE  & Navel                                 & On the navel. \\
    9  & XYPH  & Xiphoid process                       & Xiphoid process of the sternum. \\
    10 & STRN  & Sternum                               & On the jugular notch of the sternum. \\
    11 & BBAC  & Scapula                               & On the inferior angle fo the right scapular. \\
    12 & LSHO  & Left shoulder                         & Left acromion. \\
    13 & LDELT & Left deltoid muscle                   & Apex of the deltoid muscle. \\
    14 & LLEE  & Left lateral elbow                    & Left lateral epicondyle of the elbow. Upper one in the T-Pose. \\
    15 & LMEE  & Left medial elbow                     & Left medial epicondyle of the elbow. Lower on in the T-Pose. \\
    16 & LFRM  & Left forearm                          & On 2/3 on the line between the LLEE and LMW. \\
    17 & LMW   & Left medial wrist                     & On styloid process radius, thumb side. \\
    18 & LLW   & Left lateral wrist                    & On styloid process ulna, pinky side. \\
    19 & LFIN  & Left fingers                          & Center of the hand. Caput metatarsal 3. \\
    20 & RSHO  & Right shoulder                        & Right acromion. \\
    21 & RDELT & Right deltoid muscle                  & Apex of deltoid muscle. \\
    22 & RLEE  & Right lateral elbow                   & Right lateral epicondyle of the elbow. Lower one in the T-pose. \\
    23 & RMEE  & Right medial elbow                    & Right medial epicondyle of the elbow. Lower one in the T-pose. \\
    24 & RFRM  & Right forearm                         & On 1/3 on the line between the RLEE and RMW. \\
    25 & RMW   & Right medial wrist                    & On styloid process radius, thumb side. \\
    26 & RLW   & Right lateral wrist                   & On styloid process ulna, pinky side. \\
    27 & RFIN  & Right fingers                         & Center of the hand. Caput metatarsal 3. \\
    28 & LASIS & Pelvic bone left front                & Left anterior superior iliac spine. \\
    29 & RASIS & Pelvic bone right front               & Right anterior superior iliac spine. \\
    30 & LPSIS & Pelvic bone left back                 & Left posterior superio iliac spine. \\
    31 & RPSIS & Pelvic bone right back                & Right posterior superior iliac spine. \\
    32 & LGTRO & Left greater trochanter of the femur  & On the cetner of the left greater trochanter. \\
    33 & FLTHI & Left thigh                            & On 1/3 on the line between the LFTRO and LLEK. \\
    34 & LLEK  & Left lateral epicondyle of the knee   & On the lateral side of the joint axis. \\
    35 & LATI  & Left anterior of the tibia            & On 2/3 on the line between the LLEK and LLM. \\
    36 & LLM   & Left lateral malleoulus of the ankle  & The center of the heel at the same height as the toe. \\
    37 & LHEE  & Left heel                             & Center of the heel at the same height as the toe. \\
    38 & LTOE  & Left toe                              & Tip of big toe. \\
    39 & LMT5  & Left 5th metatarsal                   & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
    40 & RGTRO & Right greater trochanter of the femur & On the cetner of the right greater trochanter. \\
    41 & FRTHI & Right thigh                           & On 2/3 on the line between the RFTRO and RLEK. \\
    42 & RLEK  & Right lateral epicondyle of the knee  & On the lateral side of the joint axis. \\
    43 & RATI  & Right anterior of the tibia           & On 1/3 on the line between the RLEK and RLM. \\
    44 & RLM   & Right lateral malleoulus of the ankle & The center of the heel at the same height as the toe. \\
    45 & RHEE  & Right heel                            & Center of the heel at the same height as the toe. \\
    46 & RTOE  & Right toe                             & Tip of big toe. \\
    47 & RMT5  & Right 5th metatarsal                  & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\

>>>>

  \cprotect\caption{Descriptions of the 47 markers used in this study. The Set
    column indicates wheter the marker exists in the lower and/or full body
    marker set.  The label column matches the column headers in the
    \verb|mocap-xxx.txt| files and/or the marker map in the \verb|meta-xxx.yml|
    file.}

@@

  \begin{tabular}{lrlll}

@@

    Set & \# & Label & Name & Description \\

@@

    F   & 1  & LHEAD & Left head                             & Just above the ear, in the middle. \\
    F   & 2  & THEAD & Top head                              & On top of the head, in line with the LHEAD and RHEAD. \\
    F   & 3  & RHEAD & Right head                            & Just above the ear, in the middle. \\
    F   & 4  & FHEAD & Forehead                              & Between line LHEAD/RHEAD and THEAD a bit right from center. \\
    L/F & 5  & C7    & C7                                    & On the 7th cervical vertebrae. \\
    L/F & 6  & T10   & T10                                   & On the 10th thoracic vertbrae. \\
    L/F & 7  & SACR  & Sacrum bone                           & On the scacral bone. \\
    L/F & 8  & NAVE  & Navel                                 & On the navel. \\
    L/F & 9  & XYPH  & Xiphoid process                       & Xiphoid process of the sternum. \\
    F   & 10 & STRN  & Sternum                               & On the jugular notch of the sternum. \\
    F   & 11 & BBAC  & Scapula                               & On the inferior angle fo the right scapular. \\
    F   & 12 & LSHO  & Left shoulder                         & Left acromion. \\
    F   & 13 & LDELT & Left deltoid muscle                   & Apex of the deltoid muscle. \\
    F   & 14 & LLEE  & Left lateral elbow                    & Left lateral epicondyle of the elbow. Upper one in the T-Pose. \\
    F   & 15 & LMEE  & Left medial elbow                     & Left medial epicondyle of the elbow. Lower on in the T-Pose. \\
    F   & 16 & LFRM  & Left forearm                          & On 2/3 on the line between the LLEE and LMW. \\
    F   & 17 & LMW   & Left medial wrist                     & On styloid process radius, thumb side. \\
    F   & 18 & LLW   & Left lateral wrist                    & On styloid process ulna, pinky side. \\
    F   & 19 & LFIN  & Left fingers                          & Center of the hand. Caput metatarsal 3. \\
    F   & 20 & RSHO  & Right shoulder                        & Right acromion. \\
    F   & 21 & RDELT & Right deltoid muscle                  & Apex of deltoid muscle. \\
    F   & 22 & RLEE  & Right lateral elbow                   & Right lateral epicondyle of the elbow. Lower one in the T-pose. \\
    F   & 23 & RMEE  & Right medial elbow                    & Right medial epicondyle of the elbow. Lower one in the T-pose. \\
    F   & 24 & RFRM  & Right forearm                         & On 1/3 on the line between the RLEE and RMW. \\
    F   & 25 & RMW   & Right medial wrist                    & On styloid process radius, thumb side. \\
    F   & 26 & RLW   & Right lateral wrist                   & On styloid process ulna, pinky side. \\
    F   & 27 & RFIN  & Right fingers                         & Center of the hand. Caput metatarsal 3. \\
    L/F & 28 & LASIS & Pelvic bone left front                & Left anterior superior iliac spine. \\
    L/F & 29 & RASIS & Pelvic bone right front               & Right anterior superior iliac spine. \\
    L/F & 30 & LPSIS & Pelvic bone left back                 & Left posterior superio iliac spine. \\
    L/F & 31 & RPSIS & Pelvic bone right back                & Right posterior superior iliac spine. \\
    L/F & 32 & LGTRO & Left greater trochanter of the femur  & On the cetner of the left greater trochanter. \\
    L/F & 33 & FLTHI & Left thigh                            & On 1/3 on the line between the LFTRO and LLEK. \\
    L/F & 34 & LLEK  & Left lateral epicondyle of the knee   & On the lateral side of the joint axis. \\
    L/F & 35 & LATI  & Left anterior of the tibia            & On 2/3 on the line between the LLEK and LLM. \\
    L/F & 36 & LLM   & Left lateral malleoulus of the ankle  & The center of the heel at the same height as the toe. \\
    L/F & 37 & LHEE  & Left heel                             & Center of the heel at the same height as the toe. \\
    L/F & 38 & LTOE  & Left toe                              & Tip of big toe. \\
    L/F & 39 & LMT5  & Left 5th metatarsal                   & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
    L/F & 40 & RGTRO & Right greater trochanter of the femur & On the cetner of the right greater trochanter. \\
    L/F & 41 & FRTHI & Right thigh                           & On 2/3 on the line between the RFTRO and RLEK. \\
    L/F & 42 & RLEK  & Right lateral epicondyle of the knee  & On the lateral side of the joint axis. \\
    L/F & 43 & RATI  & Right anterior of the tibia           & On 1/3 on the line between the RLEK and RLM. \\
    L/F & 44 & RLM   & Right lateral malleoulus of the ankle & The center of the heel at the same height as the toe. \\
    L/F & 45 & RHEE  & Right heel                            & Center of the heel at the same height as the toe. \\
    L/F & 46 & RTOE  & Right toe                             & Tip of big toe. \\
    L/F & 47 & RMT5  & Right 5th metatarsal                  & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
